Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-15 robdml.tex
tex

\subsection{Selection of Source \& Destination Hardness}

@@

\subsection{Efficiency of Hardness Manipulation}

@@

@@

\subsection{Effectiveness of GA and ICS}

>>>>

\subsection{Selection of Source \& Destination Hardness}
\label{sec:41}

@@

\subsection{Efficiency of Hardness Manipulation}
\label{sec:42}

@@

Conditions for a good source and destination hardness:
%
(1) the destination hardness is semihard (or something between semihard
and softhard, we leave new sampling strategy for future work).
(2) the source hardness should have high variance and a relatively high mean
value to ensure number of benign example and number of adversarial example ratio.

\oo{Note, naive combination of benign training and adv train does not lead to better
result, why?} mix 0.5

@@

\subsection{Effectiveness of GA and ICS}
\label{sec:43}

\input{tab-gaeff.tex}

\cref{tab:gaeff}
